---
title: "p8105_hw5_zl2977"
author: "Zhourong Li zl2977"
date: "2020/11/16"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
set.seed(50)

knitr::opts_chunk$set(
 echo = TRUE,
 fig.width = 12,
 fig.height = 8,
 # fig.asp = 0.618,
 out.width = "90%")

theme_set(theme_minimal() +
  theme(legend.position = "bottom",
  # legend.title = element_blank(),
  plot.title = element_text(hjust = 0.5, size = 15),
  plot.subtitle = element_text(hjust = 0.5, size = 12)))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```




Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time.

```{r, message=FALSE, warning=FALSE}
study_df=
  tibble(
    file_names = list.files("data/p2-data/"),
    file_paths = str_c("data/p2-data/", file_names)
    )%>%
  mutate(
    data = map(file_paths, read_csv)
    )%>% #now unnest and tidy the result
  unnest(data)%>%
  separate(
    file_names, into = c("arm", "subj_id"), sep = "_"
    )%>%
  mutate(
    subj_id = str_remove(subj_id, ".csv")
    )%>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observations",
    names_prefix = "week_"
    )%>%
  mutate(
    week = as.numeric(week)
         )%>%
  select(arm, subj_id, week, observations)
  
study_df %>%
  head(10) %>% #show first 10 rows of the table
  knitr::kable()
```
   
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r, message=FALSE, warning=FALSE}

study_df%>%
  ggplot(aes(x = week, y = observations, group = subj_id, color = subj_id))+
  geom_line(size = .8, alpha = .7) + 
  geom_point(size = 1.5, alpha = .6, aes(shape = arm)) +
  facet_grid(~arm) +
  labs(title = "Spaghetti Plot",
       subtitle = "Showing Observations on each subject over time", 
       x = "week",
       y = "observations")
```
          
From the spaghetti plot above, we can see both arms have approximate observation values at beginning, the observation values in the control group do not change much over time, while the observation values in the experimental group increase over time.

## Problem 3

Create a function that produced data from normal distribution as required and conduct t-test.

```{r, message=FALSE, warning=FALSE}
sim_test=function(n = 30, mu = 0, sigma = 5){
  if (!is.numeric(mu)) {
    stop("Argument mean should be numeric")}
  sim_data =tibble(
    rnorm(n, mean = mu, sd = sigma)
  )
  test_result = t.test(sim_data, mu=0, conf.level = 0.95)
  sim_data %>%
    summarize(
    mu_hat =pull(broom::tidy(test_result),estimate),
    p_val = pull(broom::tidy(test_result),p.value)
    )
} 
```

Generate 5000 datasets for each `mu` by calling the function. Obtain the required estimates and p-values.

```{r, message=FALSE, warning=FALSE}
sim_results=
  tibble(true_mu=c(0,1,2,3,4,5,6))%>% # first mu=0, then repeat for mu=1,2,3,4,5,6
  mutate(
    output_lists = map(.x=true_mu,~rerun(5000,sim_test(mu=.x))),
    estimate_dfs = map(output_lists, bind_rows)
  )%>%
  select(
    -output_lists
  )%>%
  unnest(estimate_dfs)
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. 

```{r, message=FALSE, warning=FALSE}
sim_results %>%
  group_by(true_mu)%>%
  mutate(
    true_mu = as.factor(true_mu),
    rej = as.numeric(p_val < 0.05)
  ) %>%
  summarize(
    power=mean(rej)
  ) %>%
  ggplot(aes(x=true_mu, y =power, color = true_mu, group = true_mu))+
  ggtitle("The Power of the Tests")+
  scale_y_continuous(n.breaks = 10) +
  geom_point(size = 5, alpha = .6)+
  xlab("true value of mu")
```
                 
From the above graph we can see the power (the proportion of times the null was rejected) increases as the effect size of true mu increases. The power starts very close to 0.05 (which is our `alpha` value) when the true `mu` = 0, and then gradually approaches 1 as the the true `mu` increases towards 6.

```{r, message=FALSE, warning=FALSE}
est_all_mu_hat=
  sim_results %>%
  group_by(
    true_mu
  )%>%
  summarize(
    ave_mu_hat=mean(mu_hat)
  )%>%
  mutate(type = "all_mu_hat")

```


```{r, message=FALSE, warning=FALSE}
est_rej_mu_hat=
  sim_results %>%
  group_by(
    true_mu
  )%>%
  filter(
    p_val<0.05
  )%>%
  summarize(
    ave_mu_hat=mean(mu_hat)
  )%>%
  mutate(type = "rej_mu_hat")

```
```{r}
bind_rows(est_all_mu_hat, est_rej_mu_hat) %>%
   ggplot(aes(x=true_mu, y =ave_mu_hat, color=type))+
   ggtitle("Average Estimate Mean vs True Mean")+
   geom_point()+
   geom_path(size=3, alpha=0.5)+
   scale_x_continuous(n.breaks = 7) +
   scale_y_continuous(n.breaks = 7) +
   ylab("average estimate")+
   xlab("true value of mu")

```
                     
As the above plot shows, the sample averages of all estimated `mu_hat` are approximately equal to the true `mu`. While the sample averages of `mu_hat` across tests for which the null is rejected are not approximated equal to the true `mu`.
   
Because `rej_mu_hat` contains `mu_hat` only in samples for which null was rejected, it appears more far away from the null comparing with the values of `all_mu_hat` since `all_mu_hat` also contains samples which were failed to reject. Therefore the values of `all_mu_hat` are represented closer to the true `mu` values.
    
When the true `mu` are small, only the estimates that are significant far way from the null can be rejected, thus the average of these significantly far way estimates appeared much greater than the average of all estimates  (except true `mu` = 0 because in this case the rejected estimates appeared by equal chance in both sides of the null = 0, the average of these rejected estimates thus close to the true `mu`). 
  
However, when the true `mu` increases, the majority of the estimates are far away from the null, in other words, the majority of the estimates were being rejected, thus the difference of average between all estimates and estimates being rejected became smaller, resulting two lines got closer and closer as true values of `mu` increased.